PANNEURO_analysis

### 2020-10-27 PANNEURO_analysis_WHO_pres.Rmd

## BMI not available

>>>>

dat.raw$bmi[is.infinite(dat.raw$bmi)] = NA

dat.raw <- dat.raw %>%
  mutate(
  bmi.categories=cut(dat.raw$bmi, breaks=c(-Inf, 10, 15, 20, 25, 30, 35, 40, 45, 50, 55,  Inf), labels=c("too low","10 and less","10 to 15", "15 to 20", "20 to 25", "25 to 30", "30 to 35", "35 to 40", "40 to 45", "45 to 50", "50 to 55")))

```{r bmi_category per Sample prop per total}

bmi_category_per_Covid_prop_total <- dat.raw %>%
  count(bmi.categories, covid_probable_case_incl_screening) %>%
  mutate(Prop = round(n/sum(n), 2))

options(knitr.kable.NA = '')
kable(bmi_category_per_Covid_prop_total)
bmi_category_per_Covid_prop_total
```
```{r bmi_category per Sample prop per Sample}
bmi_category_per_Sample_prop_Sample <- dat.raw %>%
  group_by(Sample) %>%
  count(bmi.categories, Sample) %>%
  mutate(Prop = round(n/sum(n), 2))

kable(bmi_category_per_Sample_prop_Sample)
bmi_category_per_Sample_prop_Sample
```
